\documentclass[]{deedy-resume-openfont}


\begin{document}

\lastupdated

\namesection{}{Emilie Campos} { 
1109 E Grovecenter St, West Covina, CA \\
\href{mailto:ejcampos@ucla.edu}{ejcampos@ucla.edu} | 626.482.0925 | LinkedIn: \href{https://www.linkedin.com/in/ejcampos/}{ejcampos} | Github: \href{https://www.github.com/ejcampos/}{ejcampos}
}

\section{Professional Summary} 
\begin{flushleft}
UCLA Masters student in Biostatistics with a strong background in Mathematics and speaking to non-technical audiences. Strong in R programming and making detailed presentations. Seeking an interesting opportunity to apply technical background to real world.
\end{flushleft}

\section{Education} 

\runsubsection{University of California, Los Angeles}
\descript{| MS in Biostatistics} 
\location{Earned June 2019 | Los Angeles, CA $\cdot$ Cum. GPA: 4.0}
\vspace{-.25em}
\begin{tightemize} 
\item Individual Project, Statistical Computing, Biostatistics Dept: Used SAS and R to analyze a dataset of behavioral screening questionnaire answers for children. Converted a wide data set to longitudinal in order to find summary statistics. Used R to simulate similar data and wrote a function to explore how sample size and proportion of missing completely at random values affected significance.
\end{tightemize}
\sectionsep

\runsubsection{Cal Poly, Pomona} 
\descript{| BS in Applied Mathematics and Statistics}
\location{Earned December 2016 | Pomona, California $\cdot$ Cum. GPA: 3.8}
\vspace{-.25em}
\begin{tightemize}
\item Individual Project, Bayesian Data Analysis, Math Dept: Used R and Bayesian techniques to estimate the proportion of voters who voted for a fictional candidate
\item Group Leader, Statisical Consulting, Math Dept: Consulted a graduate student who was investigating the effects of various diet treatments, ages, and exposure times on the egg loads of wasps. The wasps were preying on an arachnid responsible for killing citrus trees. We used several regression techniques with and without the zero egg loads, including a zero-inflated poisson model.
\item Team Member, Statisical Consulting, Math Dept: Consulted a committee in the English Dept at CPP on whether certain evaluation techniques impacted student success. Used small samples from each college, gender, and under-represented minority status to find where improvements in intervention could be made. While we found few significant differences, it allowed the professors to focus their time.
\item Treasurer for Society for Industrial and Applied Mathematics (SIAM): managed finances for planned meetings, trips, and guest speakers; facilitated panels aimed at encouraging undergraduates to pursue graduate degrees
\end{tightemize}
\sectionsep

\section{Experience}

\runsubsection{UCLA}
\descript{| Teaching Assistant \& Graduate Student Researcher}
\location{January 2018 - present | Los Angeles, CA}
\vspace{-.25em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Teaching assistant: Lead labs in Introduction to Biostatistics for undergraduates in biological fields and nursing and labs in Introduction to Data Management and Statistical Computing for undergraduates and graduate students in computer science and biostatistics 
\item Researcher: Used principal and independent components analysis on functional data to develop an algorithm to estimate the canonical components underlying EEG signals across tasks, subjects, and electrodes. Analysis was done with simulations and with data supplied by the Semel Institute for Neuroscience and Human Behavior. This project necessitated collaboration across disciplines and effective communication. 
\end{tightemize}
\sectionsep

\runsubsection{Chaffey College \& Mt. San Antonio College}
\descript{| Tutor Expert \& Supplemental Instruction}
\location{August 2013 - December 2017 | Rancho Cucamonga, CA}
\vspace{-.25em}
\begin{tightemize}
\item Mentored new tutors, developing strategies to tutor students more effectively
\item Assisted an Elementary Statistics professor in and out of the classroom by incorporating active learning techniques
\item Tutored students both one-on-one and in small groups, encouraging a growth mindset towards mathematics, assisted physically and mentally disabled students
\item Earned CRLA Level 1 Certification
\end{tightemize}
\sectionsep

\section{Awards and Honors} 
\begin{tabular}{rll}
2019 & Abdelmonem A. Afifi Student Fellowship & UCLA \\
2019 & Student Poster Award                   & Statistical Methods in Imaging Conference \\ 
2016 & Summa Cum Laude                        & Cal Poly Pomona \\ 
\end{tabular}
\sectionsep

\section{Skills}
\begin{minipage}[t]{.6\textwidth}
\subsection{Analytical}
Statistics, \, Regression, \, Random Processes, \, Combinatorics, \, Sampling Theory and Applications, \, Modeling, \, Getting and Cleaning Data, \, Cloud Computing
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.35\textwidth}
\subsection{Computing}
R, \, SAS, \, STATA, \, \LaTeX, \, Matlab, \,  Git/Github
\end{minipage}
\end{document}