%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{EMILIE CAMPOS} % Your name
\address{1109 E Grovecenter St \\ West Covina, CA 91790} % Your secondary address (optional)
\address{(626) 482-0925 \\ ejcampos@ucla.edu}  % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Multidisciplinary engineer with excellent problem solving and critical thinking abilities, seeks hands on experience within a company that embraces creativity and innovation.Through my studies, I have gained extensive knowledge of production and manufacturing engineering, product design, among many other components of  Mechanical Engineering. Effective communicator who builds positive, cohesive relationship with all level of staff, eager to put my engineering knowledge to practical, applied use.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Ph.D., Biostatistics} \hfill {2019 - 2022}
\\ 
University of California, Los Angeles 

{\bf Master of Science (M.S.), Biostatistics} \hfill {2017-2019}\\
University of California, Los Angeles 
 
{\bf Bachelor of Science (B.S.), Applied Mathematics and Statistics} \hfill {2012 - 2016}\\
California State Polytechnic University, Pomona

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS and
INTERESTS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Skills & Production and Manufacturing Engineering, \\ 
Interests & Mechanical Part Design, Quality Control and Assurance, Flexible and Unconventional \\  & Manufacturing Systems, Metallurgy and Material Sciences.   \\  
Design Software & Autocad, ProE, SolidWorks,  Catia, ANSYS, HyperWorks. \\
Platforms &  MS Office, C.  \\
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\begin{rSubsection}{Mathematical Modeling of a Mechanical Vibration System and Solutions using Numerical Methods,}{September 2017 - Ongoing}{Major Project}{} 
\item A beneficial solution for the problems face by tractor and truck drivers.
\item Vibrational modelling and optimization of vehicle components using differential equations.
\item Providing solutions for the differential equations using numerical methods.
\item Improve Driver comfort and reduce fatigue.
\item Reduce the chance of getting affected by any orthopedic irregularities .

\end{rSubsection} 


%------------------------------------------------

\begin{rSubsection}{Friction Stir Welding of High Strength materials: Tool holder development,}{May 2017 - July 2017}{Internship project}{}
\item An Industrial Defined Project in collaboration with Institute for Plasma Research, Gujarat.
\item Development and optimization of machine tools for advanced technologies.
\item Development of manufacturing technology for usage in Plasma and Nuclear reactors.
\item Probing the possible alternative solutions of potential welding techniques.
\item Direct involvement in Space Applications Center, ISRO, Ahmedabad.

\end{rSubsection}


\end{rSection} 

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{INTERNSHIP/TRAININGS} 

{Summer Internship – Institution for Plasma Research, Gujarat.} \hfill May 2017- July 2017 \\ 
{Summer Internship, Visakhapatnam Steel Plant, RINL} \hfill June 2016 - July 2016\\

\end{rSection} 

\begin{rSection}{POSITION OF RESPONSIBILITY}

{ Head of Drafting department, KLU - MESA.} \hfill August 2016 - continuing \\
{ Coordinator and Wing Coordinator in national level technical fest YANTRIK.} \hfill 2016 and 2017 \\ 
{ Organizer and Coordinator in national technical fest SAMYAK.} \hfill 2016 and 2017\\ 
{ School Sports Captain in Class XII} \hfill April 2013 - March 2014 \\


\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular Activities} \itemsep -1pt {}   
\item Hosted and participated in YANTRIK. \hfill 2016 and 2017
\item Hosted and participated in SAMYAK. \hfill 2016 and 2017
\item Participated in International Conference on Recent Advances in Composite Materials.\hfill February 2017
\item Participated in Student Led Design Challenge, ASME in CBIT, Hyderabad \hfill October 2015 
\item Attended workshops on Catia, Hyperworks and SolidWorks \hfill September2015
\item Achieved an All India percentile of 86.9 in National Creativity Aptitude Test. \hfill March 2015
\item Won Bronze medal in Kendriya Vidyalaya Sangathan, National Sports meet in Table Tennis  \hfill October 2013 
 

\end{rSection}

\end{document}
