% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Emilie Campos O'Banion}
\newcommand{\CVTitle}{Curriculum Vitae}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{emilie-campos.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
{Department of Biostatistics, University of California, Los Angeles}
\par
\href{mailto:ejcampos@ucla.edu}
{ejcampos@ucla.edu}
\,\SubBulletSymbol\,
github: \href{https://github.com/emjcampos}{\url{emjcampos}}
\,\SubBulletSymbol\,
\href{https://emilie-campos.com}
{\url{\CVWebpage}}\\
\textit{\CVNote}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.biostat.ucla.edu}
{\textbf{University of California, Los Angeles}},
Los Angeles, California, USA

\BigGap
Ph.D. in
\href{http://www.biostat.ucla.edu}
{Biostatistics}
\hfill
\DatestampYMD{2019}{09}{23} -- present
%\DatestampYMD{2014}{07}{15}
\begin{Detail}
\SubBulletItem
Advisor:
Dr. Damla \c{S}ent\"{u}rk
\end{Detail}

\BigGap
Master of Science (M.S.) in
\href{http://www.biostat.ucla.edu}
{Biostatistics}
\hfill
\DatestampYMD{2017}{09}{23} --
\DatestampYMD{2019}{06}{14}
\begin{Detail}
\SubBulletItem
Thesis title: Principle ERP Reduction and Analysis
\SubBulletItem
Advisor: Dr. Damla \c{S}ent\"{u}rk
\end{Detail}

\BigGap
\Entry
\href{https://www.cpp.edu/sci/mathematics-statistics/index.shtml}
{\textbf{California State Polytechnic University, Pomona}}, 
Pomona, California, USA
\BigGap
Bachelor of Science (B.S.) in Applied Mathematics and Statistics
\hfill
\DatestampYMD{2012}{08}{15} --
\DatestampYMD{2016}{06}{15}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Honors \&\newline
Awards}
{Honors \& Awards}
{PDF:HonorsAndAwards}

Dissertation Year Fellowship (\$35,000) \hfill \DatestampYM{2022}{07}
\begin{Detail} 
Graduate Division, UCLA
\end{Detail}
\BigGap

Graduate Research Mentorship (\$35,000) \hfill \DatestampYM{2020}{10}
\begin{Detail} 
Graduate Division, UCLA
\end{Detail}
\BigGap

Abdelmonmen A. Afifi Student Fellowship (\$5,000) \hfill \DatestampYM{2019}{06}
\begin{Detail} 
UCLA Fielding School of Public Health 
\end{Detail}
\BigGap

Student Poster Award  (\$500) \hfill \DatestampYM{2019}{05}
\begin{Detail} 
Statistical Methods in Imaging Conference, UCI
\end{Detail}
\BigGap

Summa Cum Laude \hfill \DatestampYM{2016}{06}
\begin{Detail} 
California State Polytechnic University, Pomona
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\Entry
\href{http://www.example.com/my-institute}
{\textbf{Department of Biostatistics}},
University of California, Los Angeles

Research Assistant
\hfill
\DatestampYMD{2018}{05}{15} -- present
\begin{Detail}
\SubBulletItem
Supervisor:
Dr. Damla \c{S}ent\"{u}rk
\SubBulletItem
Research areas:
Functional data analysis, multi-task EEG.
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Organizations\newline
\& Service}
{Professional Organizations \& Service}
{PDF:ProfessionalOrganizationsService}

\SubSection
{Memberships}
{Memberships}
{PDF:Memberships}

\BigGap

ASA, ENAR, WNAR, SIAM

\BigGap

\SubSection 
{Departmental and University Committees}
{Departmental and University Committees} 
{PDF:Departmental} 

\BigGap 

Member, Society for Industrial and Applied Mathematics at CPP \hfill \DatestampY{2015} -- \DatestampY{2018}

Member, Kappa Mu Epsilon \hfill \DatestampY{2015} -- \DatestampY{2018}

\BigGap

\SubSection 
{National and International Service}
{National and International Service} 
{PDF:National} 

\BigGap 

WNAR Program Committee \hfill \DatestampY{2022}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

\SubSection
{Published and Submitted}
{Published and Submitted}
{PDF:PublishedSubmitted}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\BulletItem
Dickinson, A., \underline{Campos, E.}, \c{S}ent\"{u}rk D., Jeste S. (2021) Atypical oscillatory development during infancy in ASD. \textit{Submitted}.

\BigGap
\BulletItem 
Naples, A., \underline{Campos, E.}, \c{S}ent\"{u}rk D. (2021) Biological motion identification in children with ASD. \textit{Submitted}.

\BigGap
\BulletItem
\underline{Campos, E.}, Scheffler, A.W, Telesca, D., Sugar, C., DiStefano C., Jeste S., Levin, A.R., Naples, A., Webb, S.J., Shic, F., Dawson, G., Faja, S., McPartland, J.C., \c{S}ent\"{u}rk D., Autism Biomarkers Consortium for Clinical Trials (2022) Multilevel hybrid principal components analysis for region-referenced functional EEG data. \textit{Statistics in Medicine}, 1-21. \href{https://doi.org/10.1002/sim.9445}{\url{doi.org/10.1002/sim.9445}}

\BigGap
\BulletItem
\underline{Campos, E.}, Hazlett C., Tan P., Truong H., Loo S., DiStefano C., Jeste S., \c{S}ent\"{u}rk D. (2020) Principle ERP Reduction and analysis: Estimating and using principle ERP waveforms underlying ERPs across tasks, subjects, and electrodes. \textit{NeuroImage}, 212, 116630. \href{https://doi.org/10.1016/j.neuroimage.2020.116630}{\url{doi.org/10.1016/j.neuroimage.2020.116630}}

\endgroup

\BigGap

\SubSection
{In Preparation}
{In Preparation}
{PDF:InPreparation}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\BulletItem
\underline{Campos, E.}, Scheffler, A.W, Telesca, D., Sugar, C., DiStefano C., Jeste S., \c{S}ent\"{u}rk D. (2022) Region-referenced generalized functional linear model for longitudinal EEG data. \textit{In preparation}.

\BigGap
\BulletItem 
Schwartz, C., \underline{Campos, E.}, \c{S}ent\"{u}rk D., Jeste S. (2021) Alpha asymmetry development during the first year of life in ASD. \textit{In preparation}.

\BigGap
\BulletItem 
Daniel, M., \underline{Campos, E.}, \c{S}ent\"{u}rk D., Jeste S. (2021) Oscillatory activity in the gamma range in ASD. \textit{In preparation}.

\endgroup

\BigGap
\SubSection
{Software}
{Software}
{PDF:Software}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[8888]}

\BigGap
\BulletItem
\underline{Campos, E.}, \c{S}ent\"{u}rk D., ``mhpca: Multilevel Hybrid Principal Component Analysis," \textit{R package available on Github}, \DatestampYM{2021}{06}.

\BigGap
\BulletItem
\underline{Campos, E.}, Hazlett C., \c{S}ent\"{u}rk D., ``pERPred:  Principle ERP Reduction and Analysis," \textit{R package available on Github}, \DatestampYM{2019}{11}.


\endgroup

%%%%%%%%%%%%%%%%%%
%% PRESENTATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Presentations}
{Presentations}
{PDF:Presentations}

\SubSection
{Invited Talks}
{Invited Talks}
{PDF:Invited}

\BigGap 
\BulletItem 
\underline{Campos, E.}, Scheffler, A.W, Telesca, D., Sugar, C., DiStefano C., Jeste S., Levin, A.R., Naples, A., Webb, S.J., Shic, F., Dawson, G., Faja, S., McPartland, J.C., \c{S}ent\"{u}rk D., Autism Biomarkers Consortium for Clinical Trials (04/2021) Multilevel hybrid principal components analysis for region-referenced functional EEG data. Paper presented at the Biostatistics Department Admitted Students Day, UCLA.

\BigGap
\BulletItem 
\underline{Campos, E.}, Hazlett C., Tan P., Truong H., Loo S., DiStefano C., Jeste S., \c{S}ent\"{u}rk D. (4/2020) Principle ERP Reduction and analysis: Estimating and using principle ERP waveforms underlying ERPs across tasks, subjects, and electrodes. Paper presented at the Biostatistics Department Admitted Students Day, UCLA.
\BigGap
\BulletItem
\underline{Campos, E.}, Hazlett C., Tan P., Truong H., Loo S., DiStefano C., Jeste S., \c{S}ent\"{u}rk D. (3/2019) Principle ERP Reduction and analysis: Estimating and using principle ERP waveforms underlying ERPs across tasks, subjects, and electrodes. Paper presented at the Biostatistics Department Admitted Students Day, UCLA.

\BigGap
\SubSection
{Contributed Talks}
{Contributed Talks}
{PDF:Contributed}

\BigGap 
\BulletItem 
\underline{Campos, E.}, Scheffler, A.W, Telesca, D., Sugar, C., DiStefano C., Jeste S., Levin, A.R., Naples, A., Webb, S.J., Shic, F., Dawson, G., Faja, S., McPartland, J.C., \c{S}ent\"{u}rk D., Autism Biomarkers Consortium for Clinical Trials (06/2022) Multilevel hybrid principal components analysis for region-referenced functional EEG data. Paper presented at Western North American Region of the Internation Biometric Society Meeting, Virtual.

\BigGap
\BulletItem
\underline{Campos, E.}, Hazlett C., Tan P., Truong H., Loo S., DiStefano C., Jeste S., \c{S}ent\"{u}rk D. (3/2020) Principle ERP Reduction and analysis: Estimating and using principle ERP waveforms underlying ERPs across tasks, subjects, and electrodes. Paper presented at Eastern North American Region of the International Biometric Society Meeting, Nashville, Tennessee.


\BigGap
\SubSection
{Posters}
{Posters}
{PDF:Posters}

\BigGap 
\BulletItem 
\underline{Campos, E.}, Scheffler, A.W, Telesca, D., Sugar, C., DiStefano C., Jeste S., Levin, A.R., Naples, A., Webb, S.J., Shic, F., Dawson, G., Faja, S., McPartland, J.C., \c{S}ent\"{u}rk D., Autism Biomarkers Consortium for Clinical Trials (05/2021) Multilevel hybrid principal components analysis for region-referenced functional EEG data. Poster presented at the Statistical Methods in Imaging Conference, Emory University, Atlanta, Georgia.
\BigGap 
\BulletItem 
\underline{Campos, E.}, Hazlett C., Tan P., Truong H., Loo S., DiStefano C., Jeste S., \c{S}ent\"{u}rk D. (7/2019) Principle ERP Reduction and analysis: Estimating and using principle ERP waveforms underlying ERPs across tasks, subjects, and electrodes. Poster presented at the Joint Statistical Meetings, Denver, Colorado.
\BigGap
\BulletItem 
\underline{Campos, E.}, Hazlett C., Tan P., Truong H., Loo S., DiStefano C., Jeste S., \c{S}ent\"{u}rk D. (6/2019) Principle ERP Reduction and analysis: Estimating and using principle ERP waveforms underlying ERPs across tasks, subjects, and electrodes. Poster presented at the Statistical Methods in Imaging Conference, University of California, Irvine. \textbf{SMI Student Poster Award 2019}


%%%%%%%%%%%%%%%%%%%%%%%
%% LEADERSHIP %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Leadership}
{Leadership}
{PDF:Leadership}

%\Entry
%\href{http://ucla-bsa.netlify.com}
%{\textbf{Biostatistics Computing Club}},
%University of California, Los Angeles
%
%Founder and Organizer
%\hfill
%\DatestampYM{2020}{03} -- present
%\begin{Detail}
%\SubBulletItem
%Lead tutorials on computational methods for biostatistics students
%\SubBulletItem
%Built the BSA website using blogdown
%\end{Detail}
%\BigGap
%\Entry
%\href{https://ucla-bsa.github.io}
{\textbf{Biostatistics Student Association}},
University of California, Los Angeles

Co-President 
\hfill
\DatestampYM{2020}{07} -- \DatestampYM{2021}{09}

Vice President of Financial Affairs
\hfill
\DatestampYM{2019}{09} -- \DatestampYM{2020}{06}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEACHING %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Teaching}
{Teaching}
{PDF:Teaching}

%\Entry
%\textbf{Guest Lectures}

\BigGap
\Entry 
\textbf{Teaching Assistantships} 
\BigGap
Mathematical Statistics \hfill Winter 2022
\BigGap
Foundations of Public Health \hfill Fall 2021
\BigGap
Contemporary Health Issues \hfill Winter 2019 
\BigGap 
Introduction to Data Management and Statistical Computing \hfill Fall 2018 
\BigGap
Introduction to Biostatistics \hfill Winter 2018

\BigGap 
\Entry 
\textbf{Advising and Mentorship} 
\BigGap
\href{https://gum.ucla.edu}{Graduate-Undergraduate Mentorship (GUM) Mentor} \hfill 2020-2021
\BigGap 
\href{https://datares.github.io/#/datablog}{DataBlog Mentor} \hfill 2020-2021

\BigGap 
\Entry
\textbf{Tutoring} 
\BigGap
Tutorial Specialist, Mt. San Antonio College \hfill \DatestampYM{2016}{08} -- \DatestampYM{2018}{01}
\BigGap
Supplemental Instruction Leader, Mt. San Antonio College \hfill \DatestampYM{2017}{03} -- \DatestampYM{2017}{06}
\BigGap 
Apprentice, Chaffey College \hfill \DatestampYM{2013}{08} -- \DatestampYM{2015}{12}




%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
R, {\LaTeX}, Julia, SAS, SQL, Python

\end{document}
